Construction and Reduction of the $L_\infty$ Algebra of Observables Associated with a BV-Module

### 2025-10-23 bv-triples-main.tex
Background complete. ToninusThem updated.
Observables section - complete
Reduction Section almost done.

%- L30's ----------------------------------------------------------------------------------------------
\usepackage{quiver} %https://q.uiver.app/ % Not in Miktex!
\usetikzlibrary{nfold}
\usetikzlibrary{decorations.pathmorphing} 
\renewcommand{\Ham}{\mathrm{Ham}}
\newcommand{\Der}{\mathrm{Der}}
\usepackage{enumitem}
\setlist{topsep=0pt, leftmargin=*,label=$\bullet$}

@@

%+----------------------------------------------------------+
\section{$L_\infty$ Algebra Associated with a BV-Module}
%+----------------------------------------------------------+
	\checkpoint	
	%\input{bv-triples-Rogers-generalized}
%-----------------------------------------------------------%

%+----------------------------------------------------------+
\section{An Application: Multisymplectic Reduction}
%+----------------------------------------------------------+
	\checkpoint	
	%\input{bv-triples-reduction}
%-----------------------------------------------------------%

@@

%------------------------------------------------------------------------------------------------
% APPENDIX
%------------------------------------------------------------------------------------------------
\appendix
%------------------------------------------------------------------------------------------------
\section{Complementary Material}
	%\input{bv-triples-complementary-material}
	%\input{bv-triples-aknowledgements}
%------------------------------------------------------------------------------------------------

>>>>

%- L30's ----------------------------------------------------------------------------------------------
\usepackage{quiver} %https://q.uiver.app/ % Not in Miktex!
\usetikzlibrary{nfold}
\usetikzlibrary{decorations.pathmorphing} 
\renewcommand{\Ham}{\mathrm{Ham}}
\usepackage{enumitem}
\setlist{topsep=0pt, leftmargin=*,label=$\bullet$}

@@

%+----------------------------------------------------------+
\section{$L_\infty$ Algebra Associated with a BV-Module}
%+----------------------------------------------------------+
	\checkpoint	
	\input{bv-triples-Rogers-generalized}
%-----------------------------------------------------------%

%+----------------------------------------------------------+
\section{An Application: Multisymplectic Reduction}
%+----------------------------------------------------------+
	\checkpoint	
	\input{bv-triples-reduction}
%-----------------------------------------------------------%

@@

%-------------------------------------------------------+
\begin{frame}{Conclusion / Summary}
\begin{itemize}
  \item Algebraic formalism for $L_\infty$ observables via BV-modules.
  \item Generalizes Rogers' result.
  \item Enables reduction via constraint triples.
\end{itemize}
\end{frame}
%-------------------------------------------------------+

%-------------------------------------------------------+
\begin{frame}{Outlook}
\begin{itemize}
  \item Homotopy momentum maps.
  \item Operadic reformulation.
  \item Applications to field theory.
\end{itemize}
\end{frame}
%-------------------------------------------------------+

%-------------------------------------------------------+
% APPENDIX
%-------------------------------------------------------+
%-------------------------------------------------------+
\appendix
%-------------------------------------------------------+
%-------------------------------------------------------+
\section{Complementary Material}
	\input{bv-triples-complementary-material}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\section{References \& Aknowledgments}
%------------------------------------------------------------------------------------------------

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}[t,allowframebreaks]{Aknowledgments}
	\begin{itemize}
		\item MW reduction as "restriction to level sets", C. Lessig,
			\href{https://arxiv.org/abs/1206.3302}{arXiv:1206.3302}
		\item Several tex code snippets and slides in appendix are due to \href{https://www.ryvkin.eu/}{Leonid Ryvkin}.
		\item Some tex code snippets are due to \href{https://math.gmu.edu/~cblacke/}{Casey Blacker}.

	\end{itemize}
\end{frame}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
% https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
\begin{frame}[t,allowframebreaks]{Bibliography}
	%\nocite{*}
	\printbibliography
\end{frame}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
